---
title: "Seasonal changes in global listening habits."
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r}
library(tidyverse)
library(plotly)
library(spotifyr)
library(compmus)
```

### Introduction

In this experiment I will focus on unearthing seasonal trends in musical listenership. Using as large a slice as possible of the most popular song on Spotify on any given day of the year (if possible over the past several years to further increase the data I have to work with), I will attempt to quantify trends in genre, artist, song length, and any other statistic I where such a trend could be reasonably extrapolated.


### Dataset analysis

Placeholder text

### Visualizations 1: Basic dataset distribution

```{r}
```

*** 

Placeholder commentary: Bar graphs for genre, song length, bpm, valence, and other general analyses to pin down the distributions that exist in the dataset as a whole, as a prelude to finding seasonal trends.

### Visualizations 2: Basic seasonal changes

```{r}
```

*** 

Placeholder commentary: The same barplots as before, but now with time on the x axis. Steps (ie days per bin) to be determined by distribution of results to best show off trends.


### Visualizations 3: Region-specific trends

### Conclusions